I can see clearly now: reinterpreting statistical significance

### 2018-09-25 doc.tex

Although null-hypothesis tests have limitations, we argue here that they remain useful in many contexts as a guide to whether a certain effect can be seen \emph{clearly} in that context (e.g.
whether we can clearly see that a correlation or between-group difference is positive or negative).
We therefore suggest that p-values resulting from null-hypothesis tests be described using the language of ``statistical clarity'' rather than ``statistical significance''.
We believe that this simple linguistic change has the potential to substantially enhance clarity in statistical communication.

>>>>

Although null-hypothesis tests have limitations, we argue here that they remain useful in many contexts as a guide to whether a certain effect can be seen \emph{clearly} in that context (e.g.
whether we can clearly see that a correlation or between-group difference is positive or negative).
We therefore suggest that results of null-hypothesis tests should be described using the language of ``statistical clarity'' rather than ``statistical significance''.
We believe that this simple linguistic change has the potential to substantially enhance clarity in statistical communication.
